Parallel forecasting

### 2021-01-08 r_notebooks/parallel_forecasting.Rmd
Addibg mplus plotting functions from http://www.statmodel.com/mplus-R/

```{r, setup}
# Packages ####
library(tidyverse)
library(lubridate)
library(tsibble)
library(rstan) # needed to load prophet
library(prophet)
library(fable)
library(fable.prophet)
library(feasts)
library(furrr)
library(knitr)

@@

# Functions ####

source("../r_scripts/functions.r")

@@

```{r}
cross_validation(select(oc_gp_cluster_fcts$fits, c(regional_unit, starts_with("oc_proph"))), horizon = .5, units = "years", initial = 3)
```

@@

>>>>

```{r, setup}
# Packages ####
library(tidyverse)
library(lubridate)
library(tsibble)
library(rstan) # needed to load prophet
library(prophet)
library(fable)
library(fable.prophet)
library(feasts)
library(furrr)
library(knitr)
library(serCymruTools)

@@

@@

```{r}
cross_validation(select(oc_gp_cluster_fcts$fits, c(regional_unit, starts_with("oc_proph"))), horizon = , units = "years", initial = 3)
```

@@

## parallel joint forecasts

Why does only one part of this run in parallel?

```{r}
regionalJointFcsts <- function(data, h ="5 months"){
  regions <- unique(data$regional_unit)
  plan(multisession, gc = TRUE)
  fable_fit <-
    future_map_dfr(.x = regions,
                   .f = ~fableModels(filter(data, regional_unit ==.x)),
                   .options = furrr_options(seed = TRUE))
  message("fable fits complete")

  fable_fcst <- 
    future_map_dfr(.x = regions,
                   .f = ~as_tibble(forecast(filter(fable_fit, 
                                                   regional_unit ==.x),
                                  h = h)),
                   .options = furrr_options(seed = TRUE))
    # fable_fit %>%
    # forecast(h = h) %>%
    # as_tibble()
  message("fable forecasts complete")

  prophet_fit <-
    future_map_dfr(.x = regions,
                   .f = ~prophetModels(filter(data, regional_unit ==.x)),
                   .options = furrr_options(seed = TRUE))
  message("prophet fits complete")

  prophet_fcst <-
        future_map_dfr(.x = regions,
                   .f = ~as_tibble(forecast(filter(prophet_fit, 
                                                   regional_unit ==.x),
                                  h = h)),
                   .options = furrr_options(seed = TRUE))
    # forecast(prophet_fit, h = h) %>%
    # as_tibble()
  # Some prophet forecasts are giving daily forecasts. We want monthly forecasts.
  # This may also be influencing accuracy

  message("prophet forecasts complete")
  plan(sequential)
  # prophetModels now being run in parallel. Needed to reinstall prophet from
  # source

  joint_fcst <-
    bind_rows(fable_fcst, prophet_fcst) %>%
    mutate(lb_95 = quantile(n, .025),
           lb_80 = quantile(n, .1),
           med = median(n),
           ub_80 = quantile(n, .9),
           ub_95 = quantile(n, .975),
           sd = distributional::variance(n)^2,
           dist = n,
           n = NULL)

  return(joint_fcst)
}

system.time(regionalJointFcsts(data = dev_data))
```

84.619 seconds when opening and closing plan(multisession) over 5 regional units vs 59.108 when leaving them open
